---
title: "Lab 00 - Hello IDS!"
author: "Una Taylor"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Una", "Martha", "Charlie", 
           "Ben", "Bella", "Ferris" ),
  github_username = c("unataylor06", "marthahawksworth", "CharlieJK1", 
                      "benwebster05", "s2501383", "ferriswhynot"), 
  colour = c("lightpink", "blue", "green", 
             "blue", "blue", "black"),
  hobby = c("Reading", "Climbing", "Squash", 
            "Running", "Travelling", "Squash"),
  favourite_number = c(8, 7, 5, 4, 3, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This shows a bar graph where the y axis is the team members favorite number, the x axis is their github username, and the bar is their favorite color.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "favourite number under 10",
          title = "Lab00")
```

It is the command for labeling graphs/plots.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A nicer way of visualising this could be a table with all the listed hobbies and the number of people interested in them, or a pie chart showing the percentage of people who share a hobby.
